Evaluating infectious disease forecasts with allocation scoring rules

### 2024-01-25 alloscore_manuscript/alloscore-application-shorter.Rnw
only meaningful change here is a formatting change to make the \Sexpr render correctly for me, by moving some computation to a chunk rather than inside the expression itself.

The hospitalization data used for scoring forecasts were downloaded on \Sexpr{format(as.Date(metadata$time[which(metadata$name == "truth_data")]), "%B %d, %Y")}.

@@

For both scores, we also computed models' standardized rank among all models that submitted forecasts each week. The standardized rank is between 0 and 1, where 0 corresponds to the worst rank and 1 to the best. In the case of a tie between one or more models, all models received the better rank.

>>>>

<<>>=
download_date <- format(as.Date(metadata$time[which(metadata$name == "truth_data")]), "%B %d, %Y")
@

The hospitalization data used for scoring forecasts were downloaded on \Sexpr{download_date}.

@@

For both scores, we also computed models standardized rank among all models that submitted forecasts each week. The standardized rank is between 0 and 1, where 0 corresponds to the worst rank and 1 to the best. In the case of a tie between one or more models, all models received the better rank.
